% Compile with pdfLaTeX
\documentclass[11pt]{article}

%------------------ PACKAGES (pdfLaTeX-safe) ------------------
\usepackage[a4paper,margin=2cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{kotex}
\usepackage{makecell}
\renewcommand\cellalign{tl}   % top-left align
\renewcommand\cellgape{}      % remove extra vertical gap
% Load hyperref LAST
\usepackage[colorlinks=true,linkcolor=blue,urlcolor=blue]{hyperref}

%------------------ COLORS ------------------
\definecolor{Accent}{HTML}{1F7A8C}
\definecolor{Dark}{HTML}{12343B}
\definecolor{Muted}{HTML}{666666}

%------------------ SECTION FORMATTING ------------------
\titleformat{\section}{\Large\bfseries\color{Dark}}{}{0pt}{}
\titlespacing*{\section}{0pt}{10pt}{6pt}
\titleformat{\subsection}{\normalsize\bfseries\color{Dark}}{}{0pt}{}
\titlespacing*{\subsection}{0pt}{6pt}{4pt}

%------------------ ENTRY MACROS ------------------
% role, org, place, dates, bullets
\newcommand{\cventry}[8]{%
  \noindent\begin{tabularx}{\linewidth}{@{}p{2.5cm}X@{}}
    \textcolor{Muted}{#1} &
    \begin{minipage}[t]{\linewidth}
      \textbf{#2}\par
      \textit{#3}\par
      \textit{#4}\par
      \if\relax\detokenize{#5}\relax\else \textcolor{Muted}{#5}\par\fi
      \if\relax\detokenize{#6}\relax\else \textcolor{Muted}{#6}\par\fi
      \if\relax\detokenize{#7}\relax\else \textcolor{Muted}{#7}\fi
    \end{minipage} \\
  \end{tabularx}%
  \if\relax\detokenize{#8}\relax\else #8\fi
  \vspace{6pt}%
}

% one-line label/value
\newcommand{\cvline}[2]{\noindent\textbf{#1}\hfill #2\\}

%------------------ DOCUMENT ------------------
\begin{document}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{3pt}

%------------------ HEADER ------------------
{\Huge\bfseries Jaehyeon Moon}\\[2pt]
{\large\color{Accent}Yonsei University}\\[6pt]
{\small\color{Muted}Combined M.S. \& Ph.D. student}

\vspace{6pt}\hrule\vspace{8pt}

%------------------ CONTACT ------------------
\cvline{Email}{jhmn@yonsei.ac.kr}
\cvline{Website}{\href{https://jaehyeonmoon.github.io/}{https://jaehyeonmoon.github.io/}}
\cvline{Location}{50, Yonsei-ro, Seodaemun-gu, Seoul, Korea, 03722}

\section*{Research Interests}
\hrule
\vspace{6pt}
\begin{itemize}[left=0pt,itemsep=0pt]
    \item Deep learning models
    \item Network compression
\end{itemize}

%------------------ SECTIONS ------------------
\section*{Education}
\hrule
\vspace{6pt}
\cventry{\makecell[l]{Mar. 2020 --\\ Present}}{Yonsei University}{School of Electrical and Electronic Engineering}{Seoul, Korea}{Advisor: Bumsub Ham}{Combined M.S. \& Ph.D. student}{}{}
\vspace{10pt}

\cventry{\makecell[l]{Mar. 2016 --\\ Feb. 2020}}{Yonsei University}{School of Electrical and Electronic Engineering}{Seoul, Korea}{}{B.S. in Electrical and Electronic Engineering}{GPA: 4.06 / 4.30 (Magna Cum Laude)}{}

\section*{Publications}
\hrule
\vspace{6pt}
\begin{itemize}[left=0pt,itemsep=4pt,topsep=2pt]
  \item {\bf{Jaehyeon Moon}}\ and\ Bumsub Ham,\ "Shift-and-Sum Quantization for Visual Autoregressive Models",\ ICLR, 2026.
  \item Dohyung Kim$^{*}$,\ {\bf{Jaehyeon Moon}}$^{*}$,\ Junghyup Lee,\ Geon Lee,\ Jeimin Jeon,\ and\ Bumsub Ham,\ "Token-Based Dynamic Bit-Width Assignment for ViT Quantization",\ Pattern Recognition,\ 2026.\newline $^{*}$Equal contribution.
  \item {\bf{Jaehyeon Moon}},\ Dohyung Kim,\ Junyong Cheon,\ and\ Bumsub Ham,\ "Instance-Aware Group Quantization for Vision Transformers",\ CVPR,\ 2024.
  \item Seunghoon Lee$^{*}$,\ Jeongwoo Choi$^{*}$,\ Byunggwan Son,\ {\bf{Jaehyeon Moon}},\ Jeimin Jeon,\ and\ Bumsub Ham,\ "AccuQuant: Simulating Multiple Denoising steps for Quantizing Diffusion Models",\ NeurIPS,\ 2025. $^{*}$Equal contribution.
  \item Dohyung Kim,\ Junghyup Lee,\ Jeimin Jeon,\ {\bf{Jaehyeon Moon}},\ and\ Bumsub Ham,\ "Toward INT4 Fixed-Point Training via Exploring Quantization Error for Gradients",\ ECCV,\ 2024.
\end{itemize}

\newpage
\section*{Experiences}
\hrule
\hrule
\vspace{6pt}
\cventry{\makecell[l]{Aug. 2023 --\\ Present}}{TIPS project}{Research engineer, Articron}{}{}{Developed pruning and quantization algorithms to deploy deep neural networks on compute-in-memory (CIM) chips under the TIPS startup R\&D program}{}{}

\section*{Patents}
\hrule
\vspace{6pt}
\begin{itemize}[left=0pt,itemsep=4pt,topsep=2pt]
  \item Bumsub Ham and {\bf{Jaehyeon Moon}}, "Quantization Method and Apparatus for Visual Autoregressive Model", US-Application No. 19/548,809
  \item Bumsub Ham, {\bf{Jaehyeon Moon}}, Dohyung Kim, and Junyong Cheon, "Quantization Apparatus and Method for Artificial Neural Networks and Image Processing Device Having the Same", US-Application, 18/456,020
  \item Bumsub Ham and {\bf{Jaehyeon Moon}}, "Quantization Method and Apparatus for Visual Autoregressive Model", KR-Application No. 10-2026-0032167
  \item Bumsub Ham, Dohyung Kim, Junghyup Lee, {\bf{Jaehyeon Moon}}, Geon Lee, and Jeimin Jeon, "Token-Based Quantization Apparatus and Method for Vision Transformers", KR-Application No. 10-2024-0137421
  \item Bumsub Ham, Dohyung Kim, Junghyup Lee, Jeimin Jeon, and {\bf{Jaehyeon Moon}}, "Quantization Apparatus and Method for Artificial Neural Networks", KR-Application No. 10-2023-0116857
  \item Bumsub Ham, {\bf{Jaehyeon Moon}}, Dohyung Kim, and Junyong Cheon, "Quantization Apparatus and Method for Artificial Neural Networks and Image Processing Device Having the Same", KR-Application No. 10-2023-0072090
\end{itemize}
\vspace{6pt}

\section*{Awards \& Scholarships}
\hrule
\vspace{6pt}
\begin{itemize}[left=0pt,itemsep=4pt]
  \item National Science \& Technology Scholarships, Ministry of Science and ICT, Republic of Korea (Sep. 2018 -- Feb. 2020)
\end{itemize}

% \section*{Skills}
% \begin{itemize}[left=0pt,itemsep=3pt]
%   \item Skill 1 \hfill Advanced
%   \item Skill 2 \hfill Intermediate
%   \item Skill 3 \hfill Intermediate
% \end{itemize}

% \section*{References}
% Available upon request.

\end{document}
